Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy

### 2019-03-12 manuscript/manuscript.Rmd
Minor edits

In January 2011, the Egyptian uprisings presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state. However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy. Egypt is not alone in its non-violent crackdown on NGOs. India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes, or prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].

@@

In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes. Therefore, these INGOs are often viewed as politically motivated outsiders and they run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted. Due to the nature of the political and social issues they work on, their programmatic effectiveness is also harder to measure and quantify [@Bush:2015]. Thus, donors may believe that it is more difficult to improve respect for human rights in the target country, which limits NGOs' ability to achieve their goals.

@@

```{r child = "output/tables/tbl-likely-diffs.md"}
```

@@

```{r child = "output/tables/tbl-amount-diffs.md"}
```

@@

[^8425616]: Response 8425616.

[^6009603]: Response 6009603.

[^9526638]: Response 9526638.

>>>>

In January 2011, the Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state. However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy. Egypt is not alone in its non-violent crackdown on NGOs. India, Bolivia, Hungary, China, Russia, and others have mandated that funds cannot be used for political purposes and prohibited NGOs from accepting any funds from foreign sources [@Carothers:2015; @DPR:2015].

@@

In contrast, NGOs working on more contentious issues like human rights, election monitoring, anti-corruption, and youth movements can pose political challenges to regimes. Therefore, these NGOs are often viewed as politically motivated outsiders and run a higher risk of getting shut down [@DPR:2015], increasing the possibility of donors' resources being wasted. Due to the nature of the political and social issues they work on, their programmatic effectiveness is also harder to measure and quantify [@Bush:2015]. Thus, donors may believe that it is more difficult to improve respect for human rights in the target country, which limits NGOs' ability to achieve their goals.

@@

```{r child = "output/tables/tbl-likely-diffs.md"}

```

@@

```{r child = "output/tables/tbl-amount-diffs.md"}

```

@@
